### 2015-02-14 docs/report/code_sharing.tex

When executed in the Google Chrome console the error shown in Figure~\ref{fig:func-serialization} is thrown.
\img{Error when trying to send a Function object to a Web Worker}{../../spikes/2.2.1/test-functionSerialization/funcSerialization.png}{fig:func-serialization}

That is an expected error as explained in section 9.5.3 of the HTML standard \cite{html-whatwg}, the value being sent must support the structured clone algorithm and a Function does not meet that requirement as explained in section 2.7.5 of that same standard. It could be assumed that this is because of the challenges of serializing function closures\cite{cloud-haskell}\cite{distributed-scheme}.

@@

\subsubsection{\tstring{} serialization and tranfer benchmarks}
We created a benchmark using two functions of different length to see if the function's length affected the serialization and transfer time. We measured three approaches to transfer the string:
\begin{enumerate}
  \item Encoding the \tstring{} into a \tabuffer{} and sending it as a \code{Tranferable} and decoding it on the Web Worker.
  \item Sending the string directly
  \item Using a \code{Blob} to store the stream and retrieving that in the Worker.
\end{enumerate}

@@

\subsubsection{\tstring{} and \ttarray{} serialization and tranfer benchmarks}
We created a benchmark that tranfers a \ttarray{} and \tstring{} back and forth between the main thread an a worker to understand if transferring additional objects affected the transfer time when comparing it with just tranferring a \tstring{}.

@@

\subsubsection{Conclusion}
As the benchmarks show, the fastest way to tranfer the \tstring{} between the UI thread and workers is by directly sending it.

>>>>

When executed in the Google Chrome console the error shown in Figure~\ref{fig:func-serialization} is thrown.
\img{Error when trying to send a \code{Function} object to a Web Worker}{../../spikes/2.2.1/test-functionSerialization/funcSerialization.png}{fig:func-serialization}

That is an expected error as explained in section 9.5.3 of the HTML standard \cite{html-whatwg}, the value being sent must support the structured clone algorithm and a \code{Function} does not meet that requirement as explained in section 2.7.5 of that same standard. It could be assumed that this is because of the challenges of serializing function closures\cite{cloud-haskell}\cite{distributed-scheme}.

@@

\subsubsection{\tstring{} serialization and tranfer benchmarks}
We created a benchmark using two functions whose string representation has different lengths to see if the function's length affected the serialization and transfer time. We measured three approaches to transfer the string:
\begin{enumerate}
  \item Encoding the \tstring{} into an \tabuffer{}, sending it as a \code{Tranferable} and decoding it on the Web Worker.
  \item Sending the string directly
  \item Using a \code{Blob} to store the stream and retrieving that in the Worker.
\end{enumerate}

@@

\subsubsection{\tstring{} and \ttarray{} serialization and tranfer benchmarks}
We created a benchmark that tranfers a \ttarray{} and a \tstring{} that are properties of the same object back and forth between the main thread an a worker to understand if transferring additional objects affected the transfer time when comparing it with just tranferring a \tstring{}.

@@

\subsubsection{Conclusion}
As the benchmarks show, the fastest way to tranfer the \tstring{} between the UI thread and workers is by sending it directly.

### 2015-02-14 docs/report/micro_benchmarks.tex
Initial content on code sharing between ui and workers

\section{About Microbenchmmarks}
A common practice to measure the performance of a fragment of code, or to compare it to the performance of some other code fragment is to create a micro benchmark. Throughout this document, there are multiple references to benchmarks of this kind since their results helped us make decision about how to implement some specific library features.

@@

\begin{description}
\item[First] Be able to evalute the time it takes to perform the operation multiple times (a single one could either be too small or an outlier and the measurement could have to much variance/error).
\item[Second] Allow JIT optimizations to kick in.
\end{description}

@@

Alternatively it could notice that the variable \textit{j} is not being used so it could just throw the line away. In any case, we would just be measuring how long it takes for JavaScript to execute the loop, which is not what we want. To verify that is not the case the tool IRHydra can be used \cite{ir-hydra}, which \textit{can display intermediate representations used by V8}. As shown in the following figure, v8 inline the function (the blue chevron marks that) but the loop invariant was not detected and optimized:
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{naive_benchmark_ir_hydra}
  \caption{Optimized benchmark code with inlined function.}
\end{figure}
\pagebreak

>>>>

\section{About Microbenchmmarks}
A common practice to measure the performance of a fragment of code, or to compare it to the performance of some other code fragment is to create a micro benchmark. Throughout this document, there are multiple references to benchmarks of this kind since their results helped us make decisions about how to best implement some specific library features.

@@

\begin{description}
\item[First] Be able to evalute the time it takes to perform the operation multiple times (a single execution could either be too small or an outlier and the measurement could have too much variance/error).
\item[Second] Allow JIT optimizations to kick in.
\end{description}

@@

Alternatively it could notice that the variable \code{j} is not being used so it could just throw the line away. In any case, we would just be measuring how long it takes for JavaScript to execute the loop, which is not what we originally intended to do. To verify that is not the case the tool IRHydra\cite{ir-hydra} can be used , which \textit{can display intermediate representations used by V8}. As shown in the following figure, v8 inline the function (the blue chevron marks that) but the loop invariant was not detected and optimized:
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{naive_benchmark_ir_hydra}
  \caption{Optimized benchmark code with inlined function.}
\end{figure}
\pagebreak
